Kindly Bent to Free Us

### 2019-07-02 kindly/lang.tex
Misc fix.
Improve a bit the syntax presentation.

The syntax of \lang is presented in \cref{grammar} and follows
traditional ML languages with let bindings.
Data constructors are introduced by $\introK{K}{e}$ and eliminated
with by $\elimK{K}{e}$.
Types are composed of type variable $\tvar$, parameterized type constructors
$\T{t}$ and arrow types annotated with a kind, noted $\tau \tarr{k} \tau$.
Kinds can be either a kind variable $\kvar$, affine $\kaff$ or unrestricted $\kun$.
Type schemes and kind schemes are guarded by a set of constraints.

@@

We note $\inferSK{C}{\E}{\tau}{(\Multi k)k}$
when $\tau$ has kind $(\Multi k)k$ in environment $\E$ under constraints $C$.
The rules are shown in \cref{rules:sd-kinding}.
Kinds and types follow a small calculus with variables ($\tvar$,\dots),
functions (type constructors $\T{t}$), application ($\tapp{t}{\Multi{\tau}}$)
and primitives such as arrow ($\tau\tarr{k}\tau'$) and
borrow ($\borrowty{k}{\tau}$).
Kind inference is thus fairly straightforward and is done simply by following
the syntax of the types. The only kind arrows can appear when looking
up the kind scheme of a type constructor $\T t$. Kind arrows are forbidden
in any other contexts.

>>>>

Let us first define our conventions and meta-syntactic variables.
Expressions, types and kinds are noted respectively $e$, $\tau$, and $k$.
Variables, type variables and kind variables are noted
respectively $x$, $\tvar$ and $\kvar$. Types and kind schemes
are noted $\schm$ and $\kschm$.
In the rest of the text, we will write lists with a bar and an index, for
instance $\Multi[i]{\tau}$.
Kind constants are noted in bold capital letters, such as $\kaff$ for affine.

The syntax of \lang is presented in \cref{grammar} and follows
traditional ML languages with let bindings.
Borrows, noted $\borrow{e}$, are annotated with a specification indicating
if a borrow is immutable ($\IBORROW$) or mutable ($\MBORROW$).
We also distinguish reborrows, which are noted $\reborrow{e}$.
Match are indexed with a specification which can be either $\&^b$
(which $b$ a borrow specification) or $id$, indicating if the match
should operate on borrows or not.
Regions, noted $\region{x}{e}$ are annotated with their nesting ($n$)
and the variable whose borrow they enclose ($x$).
%
$\tapp{t}{\Multi{\tau}}$ denotes a type application where
$\T t$ is an abstract type constructor.
Arrow and borrow types are annotated with a kind, noted $\tau \tarr{k} \tau$
and $\borrowty{k}{\tau}$ respectively.
%
Kinds can be either a kind variable $\kvar$, or constants
(linear $\klin$, affine $\kaff$ or unrestricted $\kun$) indexed
by a nesting level represented by a member of $N \cup \{\infty\}$.
Type schemes and kind schemes are guarded by a set of constraints.
%
Finally, constraints are composed of a list of kind inequalities.

\TODO{Do we explain environments here, or push that for typing, later on ?}

@@

We note $\inferSK{C}{\E}{\tau}{k}$
when $\tau$ has kind $k$ in environment $\E$ under constraints $C$.
The rules are shown in \cref{rules:sd-kinding}.
Kinds and types follow a small calculus with variables ($\tvar$,\dots),
functions (type constructors $\T{t}$), application ($\tapp{t}{\Multi{\tau}}$)
and primitives such as arrow ($\tau\tarr{k}\tau'$) and
borrow ($\borrowty{k}{\tau}$).
Kind inference is thus fairly straightforward and is done simply by following
the syntax of the types. The only kind arrows can appear when looking
up the kind scheme of a type constructor $\T t$. Kind arrows are forbidden
in any other contexts.
